Selective electroporation of the viral envelope

### 2021-04-18 documents/pure_electroporation.tex
got it in one
Integral constraint failing?

@@

that is, all else being equal, the induced transmembrane voltage appears to be invariant with raw particle diameter - mildly contrary to Rjif's more detailed analysis.

>>>>

400x difference, reflected in the numerical steady state.

However, not field-time product [analytic, ].

Despite the two having nearly identical time constants, the course of the transmembrane voltage is clearly different.
[transmembrane plot here]

[gaussian pulse results, 1/2.7].

@@

that is, all else being equal, the induced transmembrane voltage appears to be invariant with particle diameter - mildly contrary to Rjif's more detailed analysis.
